\textbf{On the Common Logical Structure of Classical and Quantum Mechanics}

### 2021-06-10 Articles/2020-QuantumLogic/Source/quantumlogic.tex
QLogic: reviewed new example

To make evident why the generalization is problematic, let us add a third step. After the measurement, if the electron has $y$-spin down we will rotate by 90 degrees using the precession generated by a magnetic field, so that $x$-spin will be up. If we measure $y$-spin up, however, we do not do anything. Consider now the statements $p_f$, $q_f$ and $r_f$ that assert the same properties as before but after the third step. By construction, the electron will either have $x$-spin up or $y$-spin up, either $p_f$ or $q_f$ must be true and therefore $p_f \vee q_f = \top$. But again, this relationship is valid only after the third step, which means $p_o \vee q_o$ is not necessarily true. We could even increase the rotation to 180 degrees, such that the $y$-spin down after the measurement becomes $y$-spin up. In that case we would have $q_f = \top$. Clearly, the fact that we can construct a process that results in the condition $q_f$ to be always satisfied does not justify us to assume that the same condition is satisfied in all cases. But that is exactly what the previous generalization was doing: since after a measurement the $y$-spin is either up or down, it is always either up or down. And this does not follow. Neither the disjunction, nor its atomic components tell us anything about an inherent property associated with the observable $S_y$ possessed by a quantum particle independently of any measurement of $S_y$.

>>>>

To make evident why the generalization is problematic, let us add a third step. After the measurement of $S_y$, in the case we obtained $y$-spin down we will rotate the direction of spin by 90 degrees using the precession generated by a magnetic field, so that $x$-spin will be up. However, in the other case, when $y$-spin up is obtained, we leave the direction of spin unchanged. Consider now the statements:
\begin{description}
	\item $p_f$: ``after the third step, the electron $x$-spin is up'', 
	\item $q_f$: ``after the third step, the electron $y$-spin is up'',
	\item $r_f$: ``after the third step, the electron $y$-spin is down''.
\end{description}
\noindent that assert the same properties as before but at the later time. By construction, the electron will either have $x$-spin up or $y$-spin up, either $p_f$ or $q_f$ must be true and therefore $p_f \vee q_f = \top$.\footnote{In fact, note that $q_f$ is true if and only if $q_o$ is true, and, similarly, $p_f$ is true if and only if $r_o$ is true.} But again, this relationship is valid only after the third step, which means $p_o \vee q_o$ is not necessarily true because these statements are evaluated at different times. But this situation is formally identical to the previous one: before we had that $q_o \vee r_o \neq q_i \vee r_i$, now we have $p_f \vee q_f \neq p_o \vee q_o$. It would be improper to say that an electron has always either $x$-spin up or $y$-spin up just because it is so after the third step. In the same way, it would be improper to say that the electron as always either $y$-spin up or down just because it is so after the measurement of spin along the $y$ axis. Neither the disjunction, nor its atomic components tell us anything about an inherent property associated with the observable $S_y$ possessed by a quantum particle independently of any measurement of $S_y$.
